---
title: "GitHub Actions artifact providers"
---

workr ships built-in `"github_artifact"` load/save providers so workflow data
can pass **between CI runs**. The repo's
[`artifact-roundtrip`](https://github.com/zdz2101/workr_demoapp/blob/main/.github/workflows/artifact-roundtrip.yml)
workflow has two jobs: **produce** runs the pipeline, saves a bundle, and
uploads it with `actions/upload-artifact`; **consume** downloads it and restores
it with `LoadData = "github_artifact"` — no recomputation.

See it run on the
[Actions tab](https://github.com/zdz2101/workr_demoapp/actions/workflows/artifact-roundtrip.yml).

## The workflow

```{r}
#| code-fold: true
#| code-summary: "Show .github/workflows/artifact-roundtrip.yml"
cat(readLines(".github/workflows/artifact-roundtrip.yml"), sep = "\n")
```

## The same round-trip, live

Below reproduces the CI handoff on this build machine: produce writes a bundle,
we copy it where a download step would place it, then consume restores it.

```{r}
library(workr)

# --- produce: save a github_artifact bundle ---
snapshot_wf <- list(
  meta  = list(Type = "Snapshot", ID = "analysis"),
  steps = list(list(name = "identity", output = "ok", params = list(x = "Analysis_Summary")))
)
res <- RunProject("workflows", bRecursive = TRUE)
invisible(RunWorkflow(
  snapshot_wf, lData = res[["02_analyze"]],
  lConfig = list(SaveData = "github_artifact",
                 github_artifact = list(path = "artifact-out", artifact_name = "workr-demo-data"))
))
list.files("artifact-out/workr-demo-data", recursive = TRUE)
```

```{r}
# --- simulate upload -> download ---
unlink("artifact-in", recursive = TRUE)
dir.create("artifact-in/workr-demo-data", recursive = TRUE, showWarnings = FALSE)
file.copy("artifact-out/workr-demo-data", "artifact-in", recursive = TRUE)

# --- consume: restore via github_artifact load provider ---
restore_wf <- list(
  meta  = list(Type = "Restore", ID = "peek"),
  steps = list(list(name = "identity", output = "restored", params = list(x = "Analysis_Summary")))
)
restored <- RunWorkflow(
  restore_wf, lData = list(),
  lConfig = list(LoadData = "github_artifact",
                 github_artifact = list(
                   artifact_name = "workr-demo-data",
                   download_dir  = "artifact-in",
                   run_id        = "local",
                   artifact_fetcher = function(repo, run_id, artifact_name, download_dir, ...) {
                     file.path(download_dir, artifact_name)
                   }))
)
knitr::kable(restored, caption = "Restored from the artifact bundle")
```
