---
title: "Load & save hooks"
---

A workflow describes *what* to compute; `lConfig` **hooks** describe *where* data
comes from and goes to. The same workflow can read/write memory, local files, a
database, or CI artifacts — with no change to its steps.

`R/hooks.R` registers a `"local_files"` provider pair that persists each result
to `_artifacts/*.rds` and restores it later:

```{r}
#| code-fold: true
#| code-summary: "Show R/hooks.R"
cat(readLines("R/hooks.R"), sep = "\n")
```

## Run 1 — compute and save

```{r}
library(workr)
source("R/hooks.R")

lConfig <- list(SaveData = "local_files", artifact_dir = "_artifacts")

invisible(RunProject(strPath = "workflows", bRecursive = TRUE, lConfig = lConfig))
list.files("_artifacts", pattern = "\\.rds$")
```

## Run 2 — restore without recomputing

The load hook merges saved artifacts back into `lData` — the same mechanism the
built-in GitHub Actions artifact providers use (see [CI artifacts](ci.qmd)).

```{r}
restore_wf <- list(
  meta  = list(Type = "Restore", ID = "peek"),
  steps = list(
    list(name = "identity", output = "restored", params = list(x = "Analysis_Summary"))
  )
)

restored <- RunWorkflow(
  lWorkflow = restore_wf,
  lData     = list(),
  lConfig   = list(LoadData = "local_files", artifact_dir = "_artifacts")
)
knitr::kable(restored, caption = "Restored from _artifacts/Analysis_Summary.rds")
```
