---
title: "RunProject(): multi-phase orchestration"
---

`RunProject()` runs a directory of workflows organized into **phases** — each
immediate subfolder is one phase, run in order, with each phase's outputs
carried forward to the next.

```{r}
library(workr)
results <- RunProject(strPath = "workflows", bRecursive = TRUE)
names(results)   # keyed by phase, then by <Type>_<ID>
```

## The analysis outputs

```{r}
knitr::kable(results[["02_analyze"]][["Analysis_Summary"]],
             caption = "Analysis_Summary — mean response by treatment group")
knitr::kable(results[["02_analyze"]][["Analysis_Flagged"]],
             caption = "Analysis_Flagged — groups above the overall mean")
```

## Shaping what a phase receives — `_config.yaml`

By default every upstream output carries forward. A phase can add a
`_config.yaml` to narrow that. Here the reporting phase asks only for the
analysis-phase results:

```{.yaml filename="workflows/03_report/_config.yaml"}
input:
  from_phases: [02_analyze]
```

The assembled report object:

```{r}
str(results[["03_report"]][["Report_StudyReport"]], max.level = 1)
```

::: {.callout-note}
The `ZScore` workflow in `02_analyze` has `Active: false`, so `RunProject()`
skips it. See [Discovery](discovery.qmd).
:::
